Identifying the Tissue of Origin of Extracellular Vesicles Using RNA Expression Signatures

### 2015-09-14 poster/poster.Rnw
follow the UofI style more closely

% use this
% http://www.identitystandards.illinois.edu/graphicstandardsmanual/othermedia/posterpresentation.html
\definecolorstyle{UofI}{
  \definecolor{boldBlue}{HTML}{002058}
  \definecolor{boldOrange}{HTML}{E87722}
  \definecolor{professionalBlue}{HTML}{606EB2}
  \definecolor{professionalOrange}{HTML}{D45D00}
  }{
    \colorlet{backgroundcolor}{professionalBlue}
    \colorlet{framecolor}{black}
    \colorlet{titlefgcolor}{boldBlue}
    \colorlet{titlebgcolor}{white}
    \colorlet{blocktitlebgcolor}{professionalOrange}
    \colorlet{blocktitlefgcolor}{white}
    }
\usecolorstyle{UofI}
\definebackgroundstyle{UofIVertical}{
    \draw[line width=0pt, bottom color=backgroundcolor, 
    top color=white] (bottomleft) rectangle (topright);
}
\usebackgroundstyle{UofIVertical}
\usetitlestyle{Empty}

\makeatletter
\renewcommand\maketitle[1][]{  % #1 keys
    \normalsize
    \setkeys{title}{#1}
    % Title dummy to get title height
    \node[transparent,inner sep=\TP@titleinnersep, line width=\TP@titlelinewidth, anchor=north, minimum width=\TP@visibletextwidth-2\TP@titleinnersep]
        (TP@title) at ($(0, 0.5\textheight-\TP@titletotopverticalspace)$) {\parbox{\TP@titlewidth-2\TP@titleinnersep}{\TP@maketitle}};
    \draw let \p1 = ($(TP@title.north)-(TP@title.south)$) in node {
        \setlength{\TP@titleheight}{\y1}
        \setlength{\titleheight}{\y1}
        \global\TP@titleheight=\TP@titleheight
        \global\titleheight=\titleheight
    };

    % Compute title position
    \setlength{\titleposleft}{-0.5\titlewidth}
    \setlength{\titleposright}{\titleposleft+\titlewidth}
    \setlength{\titlepostop}{0.5\textheight-\TP@titletotopverticalspace}
    \setlength{\titleposbottom}{\titlepostop-\titleheight}

    % Title style (background)
    \TP@titlestyle

    % Title node
    \node[inner sep=\TP@titleinnersep, line width=\TP@titlelinewidth, anchor=north, minimum width=\TP@visibletextwidth-2\TP@titleinnersep]
        at (0,0.5\textheight-\TP@titletotopverticalspace) {\parbox{\TP@titlewidth-2\TP@titleinnersep}{\TP@maketitle}};

    % Settings for blocks
    \normalsize
    \setlength{\TP@blocktop}{\titleposbottom-\TP@titletoblockverticalspace}
}
\makeatother

@@

<<placenta.roc.curve,fig.width=8,fig.height=8,echo=FALSE>>=
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#1c61b6"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#008600")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Placenta Testing Set", "Placenta Training Set"),
       col=c("#1c61b6", "#008600"),
       lwd=2)
@ 
\captionof{figure}{\ac{ROC} curve of the placenta \ac{SVM}. The
  placenta \ac{SVM} is fairly effective at distinguishing between
  samples of placental origin and non-placental origin.}

@@

<<uterus.roc.curve,fig.width=8,fig.height=8,echo=FALSE>>=
ut.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["uterus"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["uterus"]][["testing"]][,"uterus"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#1c61b6"
             )
ut.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["uterus"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["uterus"]][["training"]][,"uterus"]),
              percent=TRUE,
              col="#008600")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Uterus Testing Set", "Uterus Training Set"),
       col=c("#1c61b6", "#008600"),
       lwd=2)
@ 
\captionof{figure}{\ac{ROC} curve of the uterus \ac{SVM}. The uterus \ac{SVM} is
  highly effective at distinguishing between samples of uterus origin and
  non-uterus origin}

>>>>

% use this
% http://www.identitystandards.illinois.edu/graphicstandardsmanual/othermedia/posterpresentation.html
\definecolorstyle{UofI}{
  \definecolor{boldBlue}{HTML}{002058}
  \definecolor{boldOrange}{HTML}{E87722}
  \definecolor{professionalBlue}{HTML}{606EB2}
  \definecolor{professionalOrange}{HTML}{D45D00}
  }{
    \colorlet{backgroundcolor}{professionalBlue}
    \colorlet{framecolor}{black}
    \colorlet{titlefgcolor}{boldBlue}
    \colorlet{titlebgcolor}{white}
    \colorlet{blockbodybgcolor}{white}
    \colorlet{blocktitlebgcolor}{professionalOrange}
    \colorlet{blocktitlefgcolor}{boldBlue}
    }
\usecolorstyle{UofI}
\defineblockstyle{UofIMinimal}{
    titlewidthscale=1, bodywidthscale=1, titleleft,
    titleoffsetx=0pt, titleoffsety=0pt, bodyoffsetx=0pt, bodyoffsety=0pt,
    bodyverticalshift=0pt, roundedcorners=0, linewidth=0.2cm,
    titleinnersep=1cm, bodyinnersep=1cm
}{
    \begin{scope}[line width=\blocklinewidth, rounded corners=\blockroundedcorners]
       \ifBlockHasTitle %
           \draw[draw=none,fill=blockbodybgcolor]
               (blockbody.south west) rectangle (blocktitle.north east);
           \draw[color=blocktitlebgcolor, loosely dashed]
               (blocktitle.south west) -- (blocktitle.south east);%
       \else
             \draw[draw=none,fill=blockbodybgcolor]
                 (blockbody.south west) rectangle (blockbody.north east);
        \fi
    \end{scope}
}

\useblockstyle{UofIMinimal}
\definebackgroundstyle{UofIVertical}{
    \draw[line width=0pt, bottom color=backgroundcolor, 
    top color=white] (bottomleft) rectangle (topright);
}
\usebackgroundstyle{UofIVertical}
\definetitlestyle{UofITitle}{
    width=\paperwidth, roundedcorners=0, linewidth=0pt, innersep=12mm,
    titletotopverticalspace=5mm, titletoblockverticalspace=10mm,
    titlegraphictotitledistance=10pt
}{}
\usetitlestyle{UofITitle}

\makeatletter
\renewcommand\TP@maketitle{%
   \begin{minipage}{0.8\textwidth}
        \color{titlefgcolor}
        {\bfseries \Huge \sc \@title \par}
        \vspace*{1em}
        {\huge \@author \par}
        \vspace*{1em}
        {\LARGE \@institute}
    \end{minipage}%
    \hfill
    \begin{minipage}{0.2\linewidth}
      \includegraphics[width=0.8\linewidth,height=6cm,keepaspectratio]{figures/igb_wordmark}
      \includegraphics[width=0.8\linewidth,height=6cm,keepaspectratio]{figures/uofi_mark}
    \end{minipage}
}
\makeatother

@@

<<placenta.roc.curve,fig.width=8,fig.height=8,echo=FALSE>>=
pl.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["placenta"]][["testing"]][,"placenta"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
pl.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["placenta"]][["training"]][,"placenta"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Placenta Testing Set", "Placenta Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)
@ 
\captionof{figure}{\ac{ROC} curve of the placenta \ac{SVM}. The
  placenta \ac{SVM} is fairly effective at distinguishing between
  samples of placental origin and non-placental origin.}

@@

<<uterus.roc.curve,fig.width=8,fig.height=8,echo=FALSE>>=
ut.roc.obj1 <- 
    plot.roc(as.numeric(predictions.caret.svm[["uterus"]][["testing"]][,"actual"])-1,
             as.numeric(predictions.caret.svm[["uterus"]][["testing"]][,"uterus"]),
             percent=TRUE,
             ## main="Training vs Testing set for Uterus",
             col="#002058"
             )
ut.roc.obj2 <- 
    lines.roc(as.numeric(predictions.caret.svm[["uterus"]][["training"]][,"actual"])-1,
              as.numeric(predictions.caret.svm[["uterus"]][["training"]][,"uterus"]),
              percent=TRUE,
              col="#E87722")
# testobj <- roc.test(rocobj1, rocobj2)
# text(50, 50, labels=paste("p-value =", format.pval(testobj$p.value)), adj=c(0, .5))

legend("bottomright",
       legend=c("Uterus Testing Set", "Uterus Training Set"),
       col=c("#002058", "#E87722"),
       lwd=2)
@ 
\captionof{figure}{\ac{ROC} curve of the uterus \ac{SVM}. The uterus \ac{SVM} is
  highly effective at distinguishing between samples of uterus origin and
  non-uterus origin}
